::: {.content-visible when-format="html"}

A thesis submitted for the degree of {{< meta degreetype >}} at Monash University, {{< meta affiliation >}}.

:::

# Copyright notice {-}

```{r}
#| output: asis
cat("Produced on",format(Sys.Date(), "%e %B %Y.\n\n"))
cat("© {{< meta author >}} (",format(Sys.Date(), "%Y"),").", sep="")
```

# Abstract {-}

*Do at the end. Future me problem, not current me problem.*

<!-- 
For an honours thesis, you can remove the rest of this file apart from the last couple of lines. 
-->

# Declaration {-}
I hereby declare that this thesis contains no material which has been accepted for the award of any other degree or diploma at any university or equivalent institution and that, to the best of my knowledge and belief, this thesis contains no material previously published or written by another person, except where due reference is made in the text of the thesis.

This thesis includes ?? original papers published in peer reviewed journals and ?? submitted publications. The core theme of the thesis is ??. The ideas, development and writing up of all the papers in the thesis were the principal responsibility of myself, the student, working within the Department of Econometrics & Business Statistics under the supervision of ??

(The inclusion of co-authors reflects the fact that the work came from active collaboration between researchers and acknowledges input into team-based research.)

In the case of (??insert chapter numbers) my contribution to the work involved the following:


```{r}
#| message: false
#| echo: false
library(tidyverse)
library(knitr)
library(kableExtra)
tab <- tribble(
  ~`Thesis chapter`, ~`Publication title`, ~Status, ~`Nature and % of student contribution`, ~`Nature and % of coauthors' contribution`, ~`Coauthors are Monash students`,
  2, "The Noisy Work of Uncertainty Visualisation: A Review", "Invited Contribusion", "??", "Dianne Cook, (help): ??%; Sarah Goodwin, (help): ??%; Emi Tanaka, (help): ??%; Susan Vanderplas, (help): ??%", "No"
)
```

::: {.content-visible when-format="html"}

```{r}
tab |>
  kable() |>
  row_spec(0, align = "l")
```

:::

::: {.content-visible when-format="pdf"}

```{r}
tab |>
  kable(booktabs = TRUE, format = "latex") |>
  kable_styling(full_width = TRUE, font_size = 10, latex_options = "scale_down") |>
  column_spec(1, width = "1.2cm") |>
  column_spec(c(2, 4:6), width = "2.6cm") |>
  row_spec(0, align = "l", bold = TRUE)
```

:::

I have / have not renumbered sections of submitted or published papers in order to generate a consistent presentation within the thesis.

Student name:

Student signature:

Date:

I hereby certify that the above declaration correctly reflects the nature and extent of the student’s and co-authors’ contributions to this work. In instances where I am not the responsible author I have consulted with the responsible author to agree on the respective contributions of the authors.

Main Supervisor name:

Main Supervisor signature:

Date:


#### Reproducibility statement

This thesis is written using Quarto with renv [@renv] to create a reproducible environment. All materials (including the data sets and source files) required to reproduce this document can be found at the Github repository [`github.com/harriet-mason/phd_thesis`](https://github.com/harriet-mason/phd_thesis).

This work is licensed under a [Creative Commons  Attribution-NonCommercial-ShareAlike 4.0 International License](http://creativecommons.org/licenses/by-nc-sa/4.0/).


# Acknowledgements {-}
I want to start by thanking my supervisors, who put up with my half formed ideas and complete inability to stick to deadlines for almost 4 years. You have all forever shaped the way I think about statistics, software, research, and visualisation, and for that I am incredibly grateful. To Emi and Ursula, even though you were not supervisors for the entire duration of the project, some of your feedback in the early days of my PhD had a huge influence on my approach to research, and I am grateful for your help. To Susan, having someone on the supervision team who thought the same way I did and could understand my half formed ideas well enough to help me translate them into something other people could understand, was genuinely a lifesaver and I don't think I would have finished the first paper (let alone the entire PhD) without your help. To Sarah, your exuberant energy, openness to ideas that not were not fully formed by yours truly, and your welcoming attitude to your work and lab made you an absolute joy to work with (and your joining meetings halfway between tasks made me feel better when I did it myself). To Di, I don't think I have words to express the level of gratitude I have towards you. Than you for taking me on as a research assistant, then honours student, and finally PhD student. It is not an overstatement to say I wouldn't even be in research were it not for you and whatever you saw in a random undergraduate student arguing with people in the unit forums. These last 6 years inspired a level of joy and fulfilment in my work that I didn't think I would ever see in this lifetime.

Thank you to Rachel and Alison, for your help on the third project. I had given up on the idea of doing an experiment, but your enthusiasm about the project, delightful company, and, most importantly, ability to do the parts of the research that I couldn't, allowed me to include it in my thesis. The experiment paper was easily the most fun of all the chapters in my thesis.

Thank you to Eliot for the hours we spent walking laps around the university.
into something
- phd homies
- panel
- zema/aemo
- family/friends (Sophie, tom, eliot)
- my enemies



<!--
The following line is required to re-set page numbering after preliminary material in the pdf output. Do not remove
-->

\clearpage\pagenumbering{arabic}\setcounter{page}{1}
